% Chapter 2

\chapter{Literature Review} % Main chapter title

\label{Chapter2} % For referencing the chapter elsewhere, use \ref{Chapter1} 

%----------------------------------------------------------------------------------------

\section{Concepts and Technologies used by Nukeboard}

Nukeboard.co is a software that was build with a combination of many different technologies, these technologies span across web technologies, database programming and administration, server configuration and linux administration, MVC programming paradigm and Object oriented programming. I had the some skills already before working on the project and needed to do some background research on technologies I new nothing about before fully contributing to the project and doing my own internship task.  The project was build using Object oriented PHP and MVC programming paradigm. Nukeboard run on the Laravel 4.2 framework which is a PHP web framework written on other framework. \\

Its a highly documented framework and its documentation can be found here: https://laravel.com/docs/4.2, the latest version of Laravel is 5.2. I needed to learn from the documentation anything i don't know how to use concerning the framework, in order to accomplish my intership project. In addition, I also did a background research on other technologies used in the project and I found out that Apache Tika which is an application used for Parsing PDF documents to extract the text from the PDF file and it uses Java to do its processing and the documentation can be found here: https://tika.apache.org/0.5/documentation.html, these parsing was done so that we can have a dump CV text so we can search for keywords concerning applicants for jobs in any job on nukeboard.co.

Sub-domains where highly used in nukeboard.co and it was a concept I did not really learn in school so had to do some research to understand how its implemented on servers using virtual machines and Laravel. Documenations I used to read about sub-domains can be found [x] and [x] and all these links and references will also be added to in the Reference section of these report. \\

A list of techonologies and tools used to accomplish the whole project are; PHP, HTML, CSS, CDN, Apache Tika, Laravel 4.2, MVC, jQuery, JavaScript, MySQL, phpMyAdmin, DNS Masq, SQL, Git and Github. All these technologies was used for the success of these product and to be able to work on the project, I had to learn all these various technologies in order to stand a chance. \\

\section{Similarities with other system that exist}

There exist other systems that perform a similar goal like nukeboard.co like; https://www.jobboard.io which was built mostly to suite the needs of US and other non-African countries. The merit of http://www.nukeboard.co is mostly suiting the needs of the African citizens and is built to solve the local problems of job offers in our country, this is a big difference with this sytem and other system which exist performing the same goal. \\

Another advantage that nukeboard.co has is that if there is a problem, there is a possibility to even meet in person with the nukeboard or an assistant if your problem can't be solved remotely but for other system that exists, it will be costly travelling out of the country if need be. In addition to the above mentioned, the services of nukeboard.co is cheaper than that of other system that exist like https://www.jobboard.io. In terms of pricing, Basic plan for Job Board software is: 149 dollars / month while for Nukeboard, a basic plan is free. \\

Furthermore, there is also a disadvantage about nukeboard, its build using PHP which is a technology that does not support multi threading which mean if there is more than 1 million users on the site performing operations at the same time, the through put of the application will be very high making response time to be very high to and inconviniencing the users. But Job Board was built with Multithreaded technologies that will improve on throughput and response time making the site faster to user and operations quicker.  