% Chapter 5

\chapter{Conclusion and Recommendations} % Main chapter title

\label{Chapter5} % For referencing the chapter elsewhere, use \ref{Chapter5} 

%----------------------------------------------------------------------------------------

\section{Evaluation of Internship Experience}

\subsection{Self Evaluation}

Evaluating myself, I found out that in even though I had all the skills to work on any programming project, school is complete different from industrial working environment or real life implementation of systems. I realized that its not only about coding or writing little scripts that will perform basic task in your computer. Its about engaging into many things and solving real life problem to provide solutions to the society. Engineering especially software is all about designing, analysis, implementation, maintaining of softwares to help the community grow by solving their problem to easy day to day transaction using softwares and computer programs. \\

In addition to the skills I had before starting internship, I learnt many other technologies and tricks in engineering to problem solving. Communication and working as a team which is a key aspect in engineering was also a great skill that i learnt making me able to work with others from different background of discipline like; Translators, Business Analysts, etc\ldots

In a nut shell, I will conclude by saying that the internship period was a great success and I learnt many things if I had remained in school I wouldn't have known them and also discovered many of my short comings and will make sure that I fix them so I can be better prepared myself for the job environment.

\subsection{Company Evaluation}

This part of the evaluation was done by the owner of the companay in which he filled an evaluation form provided to us by the Faculty in which we have submitted to the faculty. Over all, my evaluation from the company was a good one.

\section{General Conclusion}

To conclude, its a great idea for the facult to give engineering students internship for them to go out to the world and see how the job environment really works. From my experience, I will encourage the faculty to strictly evaluate students on internship because its an opportunity for engineering students to fix all their problems and prepare themselves for the job market. My internship was a success and I really thank everyone that contributed me in one way or the other to develop modules for Nukeboard because it was really indeed a successful one.

\section{Recommendations}

I recommend that the faculty should not change the rule of thumb that students should not do internship because will cause more harm that good since leaving school to the job market without any internship is a real disaster and can jeopardize the reputation of the company if care is not take. So I strongly recommend that internship periods should be taken really seriously because this is the only one opportunity that students have to have a directly relationship with real life companies while still a student.

\section{Furture Works on the project}

There is more work to be done on nukeboard as time goes by and most of these work will be building modules for the software and improving on the nukeboard.co core itself to support new features that will be built on it. Below is a list of up coming features that will be built into the software in the nearest future;\\

- Republishing Jobs Module. \\

- Application text dump that will is stored in the MySQL database will be well formatted and transfered to a different server were search will be done and return as JSON objects since as time goes by, the amount of CV coming in is exponentially big that MySQL database won't be able to handle.\\

- Searching CVs in nukeboard.co will be slow if the amount of CVs grow too large so a different algorithm will be used to speed up the search. A proposed algorithm already was Binary search. \\

- Nukeboard codebase will be refactored and cleaned in order to re-organize the codes and make it really easy to understand so that other developers won't face difficulty in understanding the codes. \\

- etc\ldots

\section{Other projects and work done during internship}

In addition to my work done during internship, I am really amazed at the other tasks I carried out and other technologies I learnt. A quick mention of other things I did during internship is as follows;

- Contributed Codes to Open Source Organisation in PHP(Fixed 25 bugs as of today, 15th Feb 2016). \\

- Worked on other real life projects like; http://efarm.cm(Online Agricultural Market for selling and buying of agricultural products), http://derick-tech.xyz(My Personal Website). \\

- Mentored a Google program(GCI: Google Code In) where students from 13 - 17 years old contribute to open source projects. I mentored under the WMF(Wiki Media Foundation). \\

- Did Freelancing jobs online on Upwork Global Inc and accomplished 10 jobs. \\

- Learnt how to write professional documents in LaTex which uses TeX as the scripting language. I used this technology to write my internship report.\\
